Standardized crypto-loans on\\ the Cardano blockchain

### 2021-02-04 papers/actus2021/article.tex
Responding to DK response to SJT comments.

In both cases, the prices of
cryptocurrency or electricity become a driver for the interest
rate.
However, one cannot simply take the bare price of the asset and turn
it into a rate. In order to make \emph{units of measurement} compatible
%SJT compatible with what??
adjustments should be made. Fluctuations of the interest rate driver
are embedded thus:

@@

\noindent
The \emph{spread} parameter here loosely represents the difference between
the average prime 
% SJT explain "prime" here.
% it's standard financial terminology: https://www.investopedia.com/terms/p/primerate.asp
rate that the lender expects -- the \emph{benchmark yield} -- and
the rate imposed by the driver - the higher the spread, the higher
the resulting interest rate. The multiplier %effectively 
rescales the interest rate value 
% SJT used value here rather than plot: is that OK?
% dk14 maybe "curve" would be better
in order to represent the changes to be made converting between different units
of measurement: how many rate percentage points 
% SJT percentage points of what?
% dk14 rate
you would get for a USD-to-kilowatt conversion
and so on.

In the context of ACTUS and simillar frameworks, 
% SJT - need to explain "event-based" in this context.
% dk14. "Event-driven" but it has no relation to scaling, so I'll remove it
there is
one more factor influencing interest rates thorough scaling:

@@

A counterparty might decide to reinvest profit received as interest
from the %same 
% SJT I think "same" is superfluous here: is that OK?
% dk14 sure
loan. In the simplest case, this renders as compound
interest. This can be modelled through interest accrual and capitalisation;
% SJT what does "capitalisation" mean?
% dk14 "conversion of income or assets into capital" it's quite googlable financial terms so idk if I should note it explicitly
for instance, contracts from the ACTUS specification accrue interest
between interest payments and can transfer interest to a notional
during interest capitalisation event (IPCL).

@@

\noindent
where the component \emph{receiveData} asks an oracle for Marlowe Choice if needed, and
\mbox{\emph{calculatePayoff}} calculates the payoff formula. For fixed-rate contracts
this is optimised into a pre-calculated constant function. The \emph{processPayoff} function
awaits the \texttt{Deposit} of a payoff amount from a party: if the deposit is made them 
it directs the funds to a counterparty, otherwise it transfers
the collateral to the counterparty and closes the contract. The principal components of the system are shown in Figure \ref{fig1}. There are 3 categories of components representing ACTUS functions: specification with formulas, formula wiring for fixed rates (produces precomputed payoffs) and formula wiring for variable rates (produces Marlowe-code that computes payoffs). Different types of wiring correspond to different implementations of \emph{ActusOps} implemetations (either \emph{Double} or \emph{Value}). 
% SJT added this figure ref: OK?
% Do we need to add a little more to explain Fig1?
% dk14 OK, added few sentences about Fig1

@@

Marlowe is a declarative language, and so in partticular does support mutable variables. We therefore represent the state at stage $t$ ($st_{t}$) literally through this naming convention:

>>>>

In both cases, the prices of
cryptocurrency or electricity become a driver for the interest
rate.
However, one cannot simply take the bare price of the asset and turn
it into a rate. In order to make \emph{units of measurement} compatible with each other
%SJT compatible with what??
adjustments should be made. Fluctuations of the interest rate driver
are embedded thus:

@@

\noindent
The \emph{spread} parameter here loosely represents the difference between
the average prime 
% SJT explain "prime" here.
% it's standard financial terminology: https://www.investopedia.com/terms/p/primerate.asp
rate that the lender expects -- the \emph{benchmark yield} -- and
the rate imposed by the driver - the higher the spread, the higher
the resulting interest rate. The multiplier %effectively 
rescales the interest rate curve 
% SJT used value here rather than plot: is that OK?
% dk14 maybe "curve" would be better
in order to represent the changes to be made converting between different units
of measurement: how many rate percentage points 
% SJT percentage points of what?
% dk14 rate
you would get for a USD-to-kilowatt conversion
and so on.

In the context of ACTUS and similar frameworks, 
% SJT - need to explain "event-based" in this context.
% dk14. "Event-driven" but it has no relation to scaling, so I'll remove it
there is
one more factor influencing interest rates thorough scaling:

@@

A counterparty might decide to reinvest profit received as interest
from the %same 
% SJT I think "same" is superfluous here: is that OK?
% dk14 sure
loan. In the simplest case, this renders as compound
interest. This can be modelled through interest accrual and capitalisation (conversion of income or assets into capital);
% SJT what does "capitalisation" mean?
% dk14 "conversion of income or assets into capital" it's quite googlable financial terms so idk if I should note it explicitly
for instance, contracts from the ACTUS specification accrue interest
between interest payments and can transfer interest to a notional
during interest capitalisation event (IPCL).

@@

\noindent
where the component \emph{receiveData} asks an oracle for Marlowe Choice if needed, and
\mbox{\emph{calculatePayoff}} calculates the payoff formula. For fixed-rate contracts
this is optimised into a pre-calculated constant function. The \emph{processPayoff} function
awaits the \texttt{Deposit} of a payoff amount from a party: if the deposit is made them 
it directs the funds to a counterparty, otherwise it transfers
the collateral to the counterparty and closes the contract.

The principal components of the system are shown in Figure \ref{fig1}. There are three categories of components representing ACTUS functions: specification with formulas, formula wiring for fixed rates (produces precomputed payoffs) and formula wiring for variable rates, which  produces Marlowe-code that computes payoffs. Different types of wiring correspond to different implementations of \emph{ActusOps} implementations (either \emph{Double} or \emph{Value}). 
% SJT added this figure ref: OK?
% Do we need to add a little more to explain Fig1?
% dk14 OK, added few sentences about Fig1

@@

Marlowe is a declarative language, and so in particular it does not support mutable variables. We therefore represent the state at stage $t$ ($st_{t}$) literally through this naming convention:
